\documentclass[a4paper,10pt]{article}
\usepackage[top=0.20in, bottom=0.30in, left=0.55in, right=0.85in]{geometry}
\usepackage{graphicx}
\usepackage[hidelinks]{hyperref}
\usepackage{url}
\usepackage{palatino}
\usepackage{tabularx}
\usepackage{hyperref}
\fontfamily{SansSerif}
\selectfont

\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{color}
\definecolor{mygrey}{gray}{0.75}
% \textheight=9.75in
\raggedbottom

\setlength{\tabcolsep}{0in}
\newcommand{\isep}{-2 pt}
\newcommand{\lsep}{-0.5cm}
\newcommand{\psep}{-0.6cm}
\renewcommand{\labelitemii}{$\circ$}

\pagestyle{empty}

\newcommand{\resitem}[1]{\item #1 \vspace{-2pt}}
\newcommand{\resheading}[1]{{\small \colorbox{mygrey}{\begin{minipage}{0.975\textwidth}{\textbf{#1 \vphantom{p\^{E}}}}\end{minipage}}}}
\newcommand{\ressubheading}[3]{
\begin{tabular*}{6.62in}{l @{\extracolsep{\fill}} r}
	\textsc{{\textbf{#1}}} & \textsc{\textit{[#2]}} \\
\end{tabular*}\vspace{-8pt}}
% ... [Keep all previous preamble as is] ...

\begin{document}
\hspace{0.5cm}\\[-0.2cm]

\textbf{Vinod Chandra} \\
\indent Email-id : \textbf{\url{itsvinod14@gmail.com}} \\
\indent Mobile No.: \textbf{+917455988459} \\
\indent \textbf{\href{https://github.com/VinodPandey14}{GitHub}} \ \ \textbf{\href{https://www.linkedin.com/in/vinod-pandey14/}{LinkedIn}} \ \ \textbf{\href{https://leetcode.com/u/Vinod-Pandey/}{LeetCode}} \\

\resheading{\textbf{CAREER OBJECTIVE} }\\[\lsep]
\\
\begin{itemize}
\setlength\itemsep{0.5em}
\item Enthusiastic and detail-oriented Computer Science student with a solid foundation in algorithms, full-stack development, and machine learning. Passionate about building real-world solutions through efficient coding. Seeking opportunities to grow in a dynamic environment that fosters continuous learning and impactful contributions.
\end{itemize}

\resheading{\textbf{ACADEMIC DETAILS} }\\[\lsep]
\\
\indent \rule{6.8in}{0.4pt}\\
\indent \begin{tabular}{ l @{\hskip 0.15in} l @{\hskip 0.15in} l @{\hskip 0.15in} l @{\hskip 0.15in} }
\noindent \textbf{Year} & \textbf{Degree/Exam} & \textbf{Institute} & \textbf{GPA/Marks(\%)}\\
Sep, 2022 - Present & B.TECH in Computer Science & Graphic Era Hill University,Dehradun & 8.53/10\\
2021 & 12^{th}, \ U.B.S.E & Arya Inter College Deghat & 86.00 \% \\
2019 & 10^{th},\ U.B.S.E & Arya Inter College Gurana & 90.00 \%\\
\end{tabular}
\indent \rule{6.8in}{0.4pt}

\resheading{\textbf{EXPERIENCE}}\\[\lsep]
\\
\begin{itemize}
\setlength\itemsep{0.5em}
\item \textbf{Salesforce Smartbridge Internship (Virtual)} \hfill \textit{[May 2025 – Present]}\\
Working on real-world cloud-based CRM use-cases using Salesforce tools and platforms. Gaining hands-on experience with custom object creation, workflows, reports, dashboards, and automation through Flow Builder. Developing industry-level understanding of how Salesforce supports business processes and customer relationship management. Improving practical skills in SaaS-based application development and deployment.
\end{itemize}

\resheading{\textbf{PROJECTS} }\\[\lsep]
\\
\begin{itemize}
\setlength\itemsep{0.5em}
\item \textbf{\href{https://github.com/VinodPandey14/Handwritten-Character-Recognition}{Handwritten Character Recognition}} (Jan 2025):  Built a CNN model using the EMNIST dataset for accurate handwritten character recognition, with a Flask-based web interface for real-time predictions and optimized data preprocessing.


\item \textbf{\href{https://github.com/VinodPandey14/OS-Algorithm-Visualizer}{OS Algorithm Visualizer}} (April 2025):Designed an intuitive web-based tool to visualize key OS algorithms like scheduling, memory, and disk management with real-time simulation and customizable input, built using Flask and React.

\item \textbf{\href{https://github.com/VinodPandey14/Mini-Compiler}{Mini Compiler}} (May 2025):  Developed a custom mini compiler with a dynamic grammar engine and lexical-syntax analysis using Flask and PLY, featuring a React-based interactive UI for compiling user-defined code.

\item \textbf{\href{https://compress-img.netlify.app/}{Image Compressor}} (Sep 2024): Built and deployed a web app for compressing images with minimal quality loss using Python and JavaScript.

\resheading{\textbf{TECHNICAL SKILLS} }\\[\lsep]
\begin{itemize}
\setlength\itemsep{0em}
\item \noindent \textbf{Languages}: C (proficient), C++ (proficient), Java, Python, JavaScript, HTML, PHP, SQL\\
\item \noindent \textbf{Tools}: Git \& GitHub, Linux, Windows, Render, Netlify, VS Code, Jupyter Notebooks, \LaTeX\\
\item \noindent \textbf{Frameworks}: React, NodeJS, Express, Flask, TensorFlow/Keras, scikit-learn
\end{itemize}

\resheading{\textbf{SCHOLASTIC ACHIEVEMENTS} }\\[\lsep]  
\\  
\begin{itemize}  
\setlength\itemsep{0em}  
\item \textbf{LeetCode 400+ Problems Solved:} Mastered data structures and algorithms by solving 400+ problems on LeetCode.  
\item \textbf{University-Level Coding Competitions:} Secured top positions in various algorithmic contests at Graphic Era Hill University.  
\item \textbf{Professional Presence:} Actively contributing to open-source projects on GitHub and engaging with the tech community on LinkedIn through insights, collaborations, and networking.
\end{itemize}

\resheading{\textbf{CERTIFICATIONS} }\\[\lsep]
\\
\begin{itemize}
\setlength\itemsep{0em}
\item \textbf{Google Cloud Computing: NPTEL Swayam} - Google Cloud
\item \textbf{Deep Learning Fundaments} - Elective Core
\item \textbf{Data Analytics Course} - Coursera
\end{itemize}

\end{document}
